Symbolic Dynamic Programming for Continuous State and Observation POMDPs

### 2012-06-01 cpomdp/camdp-xadd/src/doc/NIPS/draft4-10page.tex
Updated paper

We pause for a moment to make a few notes about the \texttt{PBVI}
algorithm in the context of DC-POMDPs.  If we have a fixed discrete
observation set, i.e., $forall h \, \mathcal{O}^h = \mathcal{O}$, then
the algorithm proceeds as usual, but if we have continuous observation
variables then we will need to derive a relevant set of observations
on line 10, which we describe in Section~\ref{sec:cont_obs}.  We need
to guarantee that the integral on line 14 can be done in closed-form
and we guarantee this for piecewise functions in
Section~\ref{sec:disc_obs}.  Because in general we will deal with
$\alpha$-functions represented as piecewise functions, we only assume
that strict dominance testing is implemented for \texttt{Prune} in
line 18.

@@

>>>>

We pause for a moment to make a few notes about the \texttt{PBVI}
algorithm in the context of DC-POMDPs.  If we have a fixed discrete
observation set, i.e., $\forall h \, \mathcal{O}^h = \mathcal{O}$, then
the algorithm proceeds as usual, but if we have continuous observation
variables then we will need to derive a relevant set of observations
on line 10, which we describe in Section~\ref{sec:cont_obs}.  We need
to guarantee that the integral on line 14 can be done in closed-form
and we guarantee this for piecewise functions in
Section~\ref{sec:disc_obs}.  Because in general we will deal with
$\alpha$-functions represented as piecewise functions, we only assume
that strict dominance testing is implemented for \texttt{Prune} in
line 18.

@@

%\vspace{-2mm}
